---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# acPCoA

<!-- badges: start -->
<!-- badges: end -->

AC-PCoA is a method proposed by Yu Wang etc., which reduces the data 
    dimension while extracting the information from different distance measures using  principal 
    coordinate analysis (PCoA), and adjusts the  confounding factors across multiple data sets  
    by minimizing  the  associations  between  the  lower  dimensional  representations and the 
    confounding variables. Application of the proposed method is further extended to  the 
    scenario of classification and prediction.

## Installation

To install "acPCoA", first you need to install the P package "acPCA" from https://github.com/linzx06/AC-PCA

Then, you can install the released version of "acPCoA" from github with

```{r}
#install.packages("devtools")
#library(devtools)
#install_github("YuWang28/acPCoA")
```

## Example

This is a basic example which shows you how to implement acPCoA for visualization after confounding factor adjustment:

```{r example}
library(acPCoA)
library(ggplot2)
X <- data_mbqc_groupA$DistMat.BC;
Y <- data_mbqc_groupA$ConfounderMat;
result_acPCoA <- acPCoA(DistanceMatrix=X, ConfounderMatrix=Y, nPC=2, lambda=seq(0, 20, 0.05), kernel="linear")
ggplot(as.data.frame(result_acPCoA$Xv),aes(x=V1,y=V2,color=data_mbqc_groupA$Specimen))+geom_point()
```



